### 2020-05-06 serial.tex

During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population):
\begin{equation}
\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) g(\tau) \dtau.
\end{equation}
Analogous to the intrinsic generation-interval distribution, 
forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to link $r$ and \Ro in the same way as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
\begin{equation}
\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
\end{equation}
where the initial forward serial-interval distribution is given by:
\begin{equation}
f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) k(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
\end{equation}
In the Appendix, we provide a mathematical proof of this relationship.
\jd{$k$ for marginal density is really slowing me down (since Champredon uses k for Rg). Maybe that's just my problem, but maybe we can think of a better letter.}

>>>>

During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population):
\begin{equation}
\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) g(\tau) \dtau.
\end{equation}
Analogous to the intrinsic generation-interval distribution, 
forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same value of \Ro for a given $r$ as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
\begin{equation}
\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
\end{equation}
where the initial forward serial-interval distribution is given by:
\begin{equation}
f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) k(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
\end{equation}
In the Appendix, we provide a mathematical proof of this relationship.
\jd{$k$ for marginal density is really slowing me down (since Champredon uses k for Rg). Maybe that's just my problem, but maybe we can think of a better letter.}
